Analysis of Competence Index

### 2017-05-10 analysis/analysis_competence.Rmd
update references and include equations

---
title: "Analysis of Competence Index"
author: "AJ Perez-Luque (@ajpelu)"
date: "2017 Feb"
output:  
  md_document:
    variant: markdown_github
---

@@

The following competition indices were computed: 
### Basal Area

$$ \sum_{i=1}^{n}pi\cdot (dbh_{i} / 2)^2 $$

* Get unique identifier of focal tree 
* Competence indexes: 
    *

@@

  ## Number of competitors with dn_j > dn_i (focal tree)
  n_competitors_hihger <- df %>%
    filter(sp != 'Focal') %>%
    filter(dn > dnft) %>% 
    count() %>% 
    transmute(n_competitors_hihger = n)

@@

  df_indices <- df_more_indices %>% 
    summarise(ba = sum(basal_area),
              srd = sum(size_ratio_distance),
              sdd = sum(size_diff_distance),
              nesr = sum(neg_exp_size_ratio),
              newsr = sum(neg_exp_w_size_ratio),
              lorimer = sum(lorimer),
              crowding = sum(crowding)) %>% 
    mutate(nc = n_competitors,
           nch = n_competitors_hihger,
           pd = plot_density,
           std = stand_density,
           ss = sum_sizes,
           sr = size_ratio,
           dnn = dist_nn,
           id_focal = focal_trees[[i]])

@@

rm(n_competitors, n_competitors_hihger, plot_density, stand_density, sum_sizes, size_ratio, dist_nn, df, df_indices, output, df_more_indices, dnft)

@@

>>>>

---
title: "Analysis of Competence Index"
author: "AJ Perez-Luque (@ajpelu)"
date: "2017 Feb"
output:  
  md_document:
    variant: markdown_github
bibliography: references.bib 
csl: ecology.csl
---

@@

The following competition indices were computed. See @GeaIzquierdo2009 for more info.

### Distance-Independet Indices

* Basal Area (**ba**)

$$ BA = \sum_{i=1}^{n}pi\cdot (dbh_{i} / 2)^2 $$

* Stand Density (**std**)

$$ std = n_{trees} / \mathrm{plot\, area(ha)} $$

* Plot Density (**pd**)

$$ pd = n_{trees} / \mathrm{plot\, area}$$

* Number of competitors (**n_competitors**): number of competitors within *r* meters (10 m)

* Number of competitors higher (**n_competitors_higher**): number of competitors within *r* meters (10 m) such that $ dbh_j > dbh_i $

* Sum of size (**sum_sizes**) of trees within *r* meters (10 m): $ \sum dbh_{j} $

* Size ratio (**sr**)

$$ sr = dbh_i / \sum_{i=1}^{n}dbh_i $$

### Distance-Dependet Indices

* Distance to nearest tree (**dnn**)

* Crowding

$$ \mathrm{crowding} = \sum_{i=1}^{n}(dbh_i / dist_{ij}) $$

* Lorimer

$$ \mathrm{lorimer} = \sum_{i=1}^{n}\left [ (dbh_i / dbh_i) / \sqrt{dist_{ij}/r} \right ] $$

* Negative Exponential size ratio (**nesr**)

$$ \mathrm{nesr} = \sum_{i=1}^{n} (dbh_j / dbh_i) \cdot \left[ 1 / \exp(dist_{ij} + 1) \right ] $$

* Negative Exponential Weighted size ratio (**newsr**)

$$ \mathrm{newsr} = \sum_{i=1}^{n} (dbh_j / dbh_i) \cdot \exp\left[ (-dist_{ij} + 1) / (dbh_i + dbh_j) \right ] $$

* Size ratio proportional to distance (**srd**)

$$ \mathrm{srd} = \sum_{i=1}^{n} (dbh_j / dbh_i) \cdot \left[1/ (dist_{ij} + 1) \right ] $$

* Size difference proportional to distance (**sdd**)

$$ \mathrm{sdd} = \sum_{i=1}^{n} \left[ (dbh_j  - dbh_i) / (dist_{ij} + 1) \right ] $$

@@

  ## Number of competitors with dn_j > dn_i (focal tree)
  n_competitors_higher <- df %>%
    filter(sp != 'Focal') %>%
    filter(dn > dnft) %>% 
    count() %>% 
    transmute(n_competitors_higher = n)

@@

  df_indices <- df_more_indices %>% 
    summarise(ba = sum(basal_area),
              srd = sum(size_ratio_distance),
              sdd = sum(size_diff_distance),
              nesr = sum(neg_exp_size_ratio),
              newsr = sum(neg_exp_w_size_ratio),
              lorimer = sum(lorimer),
              crowding = sum(crowding)) %>% 
    mutate(n_competitors,
           n_competitors_higher,
           pd = plot_density,
           std = stand_density,
           sum_sizes,
           sr = size_ratio,
           dnn = dist_nn,
           id_focal = focal_trees[[i]])

@@

rm(n_competitors, n_competitors_higher, plot_density, stand_density, sum_sizes, size_ratio, dist_nn, df, df_indices, output, df_more_indices, dnft)

@@

## References
